On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2019-03-28 docs/mvfits_paper/mvf.tex
Refactor indexing in Alg. 4 psudocode [10]

    \State Calculate $\alpha^{(1)}_k$ via \eqn{eq:pinv3}. Implicitly, $n=1$.
    \State Calculate the current model prediction $g^{(1)}$ via \eqn{eq:rat4}.
    \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = ||var(g^{(n)} - g^{(0)})||/||g^{(0)}||$, where $var$ is the variance.
    \State $done = False$

@@

      \State Calculate $\alpha^{n+1}_{k}$  via \eqn{eq:pinv3}.
      \State Calculate the current model prediction $g^{(n)}$ via \eqn{eq:rat4}.
      \State Calculate the model representation error, e.g. $\epsilon^{(n)} = ||g^{(n)} - g^{(0)}||/||g^{(0)}||$.
      \State $done = |\epsilon^{(n-1)}-\epsilon^{(n)}| < tol$
      \State (Implicitly, $n = n+1$)

>>>>

    \State \textbf{Let} $n=0$
    \State Calculate $\vec{\alpha}^{(1)}$ via \eqn{eq:pinv3}.
    \State Calculate the model prediction $\vec{g}^{(1)}$ via \eqn{eq:rat4}.
    \State Calculate the model representation error $\epsilon^{(1)}$.
    \State \textbf{Let} $done = False$

@@

      \State $n=n+1$
      \State Calculate $\vec{\alpha}^{(n+1)}$  via \eqn{eq:pinv3}.
      \State Calculate the model prediction $\vec{g}^{(n+1)}$ via \eqn{eq:rat4}.
      \State Calculate the model representation error $\epsilon^{(n+1)}$.
      \State $done = |\epsilon^{(n)}-\epsilon^{(n+1)}| < tol$
